---
title: "Statistics2_Assignment3_PolyzogopoulosPavlos_BAPT1730"
author: "pavlos"
date: "22 Απριλίου 2018"
output: html_document
---

## Question 1 

```{r}
d1 <- c(1, 0, 0, 1, 0, 0, 0, 1)
d2 <- c(0, 1, 0, 1, 1, 0, 0, 0)
d3 <- c(0, 0, 1, 0, 0, 0, 1, 0)
d4 <- c(0, 0, 0, 1, 0, 0, 0, 0)
d5 <- c(0, 0, 0, 0, 0, 0, 1, 0)
d6 <- c(0, 0, 0, 1, 0, 1, 0, 1)
d7 <- c(0, 0, 1, 0, 0, 1, 0, 1)
d8 <- c(1, 0, 0, 0, 0, 0, 0, 1)
d9 <- c(0, 0, 0, 0, 0, 1, 0, 1)
d10 <- c(1, 1, 0, 0, 0, 1, 0, 1)
nb_df <- as.data.frame(rbind(d1,d2,d3,d4,d5,d6,d7,d8,d9,d10))
names(nb_df) <- c("BadCredit", "HasStableJob", "OwnsHouse", "BigLoan",
"HasLargeBankAccount", "HasPriorLoans", "HasDependents", "Decision")



```

## Question 2

```{r}



countPositive <- length(which(nb_df$Decision == 1))
countNegative <- length(which(nb_df$Decision == 0))
probabilityPositive <- countPositive/ nrow(nb_df)
probabilityNegative <- countNegative/nrow(nb_df)
priors <- c(probabilityNegative,probabilityPositive)
print(priors)

```

## Question 3

```{r}

BadCredit1 <- c(0,0)
HasStableJob1 <- c(0,0)
OwnsHouse1 <- c(0,0)
BigLoan1 <- c(0,0)
HasLargeBankAccount1 <- c(0,0)
HasPriorLoans1 <- c(0,0)
HasDependents1 <- c(0,0)

summary_df <- data.frame(BadCredit1, HasStableJob1, OwnsHouse1, BigLoan1, HasLargeBankAccount1, HasPriorLoans1, HasDependents1)

for (i in 1:7){
  
  summary_df[1,i] <- round(nrow(nb_df[which(nb_df[,i]==1 & nb_df[,8]==0),])/length(which(nb_df[,8] == 0)),2)
  summary_df[2,i] <- round(nrow(nb_df[which(nb_df[,i]==1 & nb_df[,8]==1),])/length(which(nb_df[,8] == 1)),2)}

summary_df$Decision <- c(0,1)
summary_df

```

The output vector contains, in the first row  the probabilities P(Fi = 1|Class = 0) and 
in the second the probabilities P(Fi = 1|Class = 1).

## Question 4

These are the probabilitites  P(Fi = 1|C) meaning that trere are the probabilities of a feature being 1 (value 1) given the class.
we could also compute P(Fi = 0|C) if we wanted the sum of each column to add up to 1
  

## Question 5

In order to calculate the probabilities P(Fi = 0|C) we could just substract each probability from 1. 
For example the probability that the bank will decide to give out a loan (Decision=0) when the customer owns a house (OwnsHouse=0) is
P(OwnsHouse = 0|C=0) = 1 - P(OwnsHouse = 1|C=0) = 1-0.17 = 0.83.


## Question 6a

Likewise the probability that the bank will decide to give out a loan (Decision=0) when the customer has a bad credit score (BadCredit=0) is
P(BadCredi=0|C=0) = 1 - P(BadCredi=1|C=0) = 1 - 0 = 1.

## Question 6b

The following code will produce a dataframe which is going to have all the smoothed probabilities.
These would be P(Fi=0|C) and P(Fi=1|C).


```{r}
BadCredit <- c(0,0,0,0)
HasStableJob <- c(0,0,0,0)
OwnsHouse <- c(0,0,0,0)
BigLoan <- c(0,0,0,0)
HasLargeBankAccount <- c(0,0,0,0)
HasPriorLoans <- c(0,0,0,0)
HasDependents <- c(0,0,0,0)

summary_df_pred <- data.frame(BadCredit, HasStableJob, OwnsHouse, BigLoan, HasLargeBankAccount, HasPriorLoans, HasDependents)
rownames(summary_df_pred) <- c("Feature1C0","Feature1C1","Feature0C0","Feature0C1")

for (i in 1:7){
  
  summary_df_pred[1,i] <- round((nrow(nb_df[which(nb_df[,i]==1 & nb_df[,8]==0),])+1)/(length(which(nb_df[,8] == 0))+2),2)
  summary_df_pred[2,i] <- round((nrow(nb_df[which(nb_df[,i]==1 & nb_df[,8]==1),])+1)/(length(which(nb_df[,8] == 1))+2),2)
  summary_df_pred[3,i] <- round((nrow(nb_df[which(nb_df[,i]==0 & nb_df[,8]==0),])+1)/(length(which(nb_df[,8] == 0))+2),2)
  summary_df_pred[4,i] <- round((nrow(nb_df[which(nb_df[,i]==0 & nb_df[,8]==1),])+1)/(length(which(nb_df[,8] == 1))+2),2)
}
summary_df_pred

```

## Question 7


```{r}
PredValue0 <- 1
PredValue0[1:10] <- 1

PredValue1 <- 1
PredValue1[1:10] <-  1

Class0 <- 1
Class0[1:10] <- 1

Class1 <- 1
Class1[1:10] <- 1

PredDecision<-0
PredDecision[1:10] <- 0
```

Implement the function

```{r}
predict_nb <- function(test_df, priors, prob_matrix) {
  
  for (i in 1:10){
    
    for (j in 1:7){
      
      if(test_df[i,j]==1){
        PredVal0 <- prob_matrix[1,j]
        PredVal1 <- prob_matrix[2,j]}
        
      else 
      {
        PredVal0 <- prob_matrix[3,j]
        PredVal1 <- prob_matrix[4,j]}
      
      PredValue0[i] <- PredValue0[i] * PredVal0
      PredValue1[i] <- PredValue1[i] * PredVal1
    }
    
    Class0[i] <- PredValue0[i] * priors[1]
    Class1[i] <- PredValue1[i] * priors[2]
    
    if(Class0[i]>Class1[i]){
      PredDecision[i] <- 0 }
    
    else
    {
      PredDecision[i] <- 1}
    }
  
  print(PredDecision)}
  
```


##Question 8

Test the training accuracy of the Naive Bayes Model (using the same dataset for training and testing)

```{r}
Predicte_Decision <- predict_nb(nb_df,priors,summary_df_pred)

table(nb_df$Decision,Predicted_Decision)
Accuracy <- (mean(nb_df$Decision==Predicted_Decision)) *100

print(paste("Model Accuracy:",Accuracy,"%"))
```
